\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\input{rust.tex}
\title{Algorithms for Public Transit Graphs}
\author{Joshua Wong, Kyler Chin, Jaiveer Gahunia}
\author{
  \small Joshua Wong \\
  \small Catenary Maps \\
  \small \texttt{admin@catenarymaps.org}
  \and
  \small Kyler Chin \\
  \small Catenary Maps \\
  \small \texttt{kyler@catenarymaps.org}
  \and Jaiveer Gahunia
  \and Chelsea Wen
}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
These algorithms will be used to construct a public transit system as a graph.
We will use the WGS84 coordinate system and represent the Earth as an oblate spheroid. The difficulty in these problems comes from the issue of the Earth's irregular shape.
\section{Point-Geodesic Problem}
The problem states: Given a Geodesic, defined by the shortest path between two points on a sphere's surface, and a random point on the sphere's surface, find the closest point on that line to that random point.
\subsection{Solution in Euclidean Space}
Take Points $A$ and $B$, and parametrize $\overline{AB}$ to create a function of a vector, $f(t)$. Derive $f(t)$ to find the critical point, $t_c$. The closest point will be $f(t_c)$.
\subsection{Kyler's Solution}
Take the Geodesic's endpoints $(P_1, P_2)$, along with the random point, $R_1$, and construct $\triangle{P_1P_2R_1}$, using Vincenty's formulae to construct the edges. Then, take the midpoint of $\overline{P_1P_2}$, and construct a new line using this new midpoint, $M_1$, and $R_1$. Throw out whichever line is longer $\overline{R_1P_1}$ or $\overline{R_1P_2}$, and replace it with $\overline{R_1M_1}$. Repeat this process until $\overline{P_1P_2}$ is within the specified tolerance. This algorithm is $O(\log_2(n))$, where $n$ is equal to the original length of $\overline{P_1P_2}$. It takes $\log_2(n)$ steps to reach the specified tolerance.
\subsection{Final Solution}
We just ended up using Baselga and Martínez-Llario's Solution on this problem \cite{Baselga2018}, with Karney's improvements. \cite{karney2023geodesic}
\bibliographystyle{IEEEtran}
\bibliography{algo.bib}


\end{document}
